Predictive modeling with cross validation (this file is a mess)

### 2017-08-27 model fitting/cross_validation.Rmd
deleted code

train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]

train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]

train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]

train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]

train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
```

@@

```{r}
library(rms)
model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_all_lower + update + prior_effort + ampm + weekday + rcs(device_length, 5) + sqrt(avg_tag_score) + rcs(text_length, 3) + rcs(avg_tag_length, 3) + rcs(newline_ratio, 3), data = train1)
AIC(model, k = 2) # 64977.65
# with cph fits, keep getting errors with predict function 
```

@@

```{r}
# working with model_spline2 (model with all splines)
train1$predictions <- predict(object = full , type = "risk")
performance <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)
performance

@@

### FINAL MODEL (?)
```{r}
# final <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
#     contain_unanswered + title_questionmark + sqrt(avg_tag_score) + 
#     text_all_lower + update + prior_effort + ampm + weekday + 
#     pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, 
#     df = 0, method = 'AIC'), data = x)
# summary(final)
# AIC(final, k = 2) # 82957.53

full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + ampm + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + pspline(text_length, 3) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3), data = x)
AIC(full, k = 2) # 82974.66

x$predictions <- predict(full, type = "risk")
performance <- cph(Surv(time_until_answer, answered) ~ predictions, data = x)
AIC(performance, k = 2) # 83243.04

final_metrics <- data.frame(HR = exp(performance$coefficients), 
                              LR = round(performance$stats[3],2), 
                              pval = round(performance$stats[5],2), 
                              AIC = stats::AIC(performance, k = 2),
                              Dxy = round(performance$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
final_metrics
# performance metrics on entire data set are not different from cross validation 
```

@@

### residuals, PH assumption

```{r, residuals, echo = FALSE}
full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + title_beginwh + text_contain_punct + text_all_lower + update + greeting + n_tags + gratitude + prior_effort + strata(ampm) + weekday + n_images + sqrt(avg_tag_score) + pspline(device_length, df = 5) + poly(text_length, 2) + pspline(avg_tag_length, 3) + pspline(newline_ratio, 3), data = train1)
# If i fit text_length with poly (orthogonal polynomial), text_length doesn't violate ph anymore 
#=============================================
#martingale residuals
# plot for each continuous predictor, assess adequacy of functional form of predictors, or suggest a potential form 
train1$mart <- residuals(full, type = "martingale")
train1$sqrt_score <- sqrt(train1$avg_tag_score)

ggplot(train1, aes(x = sqrt_score, y = mart)) + 
  geom_point() + 
  geom_smooth() + 
  ggtitle(paste("Martingale Residuals for device_length")) + 
  scale_x_continuous("Device_length")
# what do I assess for spline variables?

#=============================================
# deviance residuals 
# check for outliers identify questions poorly predicted by the model

train1$deviance <- residuals(full, type = "deviance")
plotly::ggplotly(ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
  geom_point() + 
  scale_x_continuous("Question index") + 
  scale_y_continuous(breaks = seq(-4, 4, by = 0.5)) + 
  ggtitle("Deviance Residuals"))
# quite a few questions have a deviance residual of larger than 2.5 (use ggplotly to identify)

# looking at points with deviance residuals > |2.5| (suggested in 417 notes)

# only 2 of these outliers were not answered

#=============================================

spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
# schoenfeld residuals
schoen <- as.data.frame(residuals(full, type = "schoenfeld"))
# complete event times sorted from shortest to longest
schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)

plot_schoen <- function(var) {
  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
    geom_point() + 
    geom_smooth(method = "loess") + 
    ggtitle(paste("Schoenfeld Residuals for", var)) + 
    scale_y_continuous("Residuals")
}
names <- names(schoen)[-ncol(schoen)]
purrr::map(names, plot_schoen)

plotly::ggplotly(plot_schoen("ampmMorning")) # comptime 2020.89 (id = 390866) is pulling it up? 
plotly::ggplotly(plot_schoen("new_categoryApple Product")) # same question
plotly::ggplotly(plot_schoen("ps(text_length)8")) # same question
plotly::ggplotly(plot_schoen("title_questionmarkTRUE")) # same question!!! 
# plots indicate that new_user, ampm and a few others may have violated ph assumption

#=============================================
# formal test of PH assumption
options(scipen=999)
ph_test <- data.frame(predictors = rownames(cox.zph(spline5)$table), cox.zph(spline5)$table) 
rownames(ph_test) = NULL
ph_test <- ph_test %>%
  arrange(p)

# plots of variables that violated PH assumption in cox.zph test
plot_schoen("new_categoryApple Product")
plot_schoen("new_categoryElectronics")
plot_schoen("new_categoryCamera")
plot_schoen("new_categoryGame Console")
plot_schoen("title_questionmarkTRUE")

#=============================================
# score residuals: check for influential observations. ID quesitons who's predictor values highly effect
score <- as.data.frame(residuals(full, type = "score"))

# function to plot score residuals
plot_score <- function(column) {
  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Score residuals for", column)) + 
    scale_y_continuous("Score Residuals") + 
    scale_x_continuous("Question index")
}
columns <- names(score)
purrr::map(columns, plot_score)
# score residuals show that there are quite a few points that may be influential (check with ggplotly)
```

>>>>

train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
```

@@

```{r}
library(rms)
model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_all_lower + update + prior_effort + ampm + weekday + rcs(device_length, 5) + sqrt(avg_tag_score) + rcs(text_length, 3) + rcs(avg_tag_length, 3) + rcs(newline_ratio, 3), data = train1)
AIC(model, k = 2) # 64977.65
```

@@

```{r}
train1$predictions <- predict(object = full , type = "risk")
performance <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)
performance

@@

@@
